\documentclass[12pt]{constitution}
\usepackage{mathpazo}

\begin{document}

\title{Constitution of the Stevens Institute of Technology Cyber Defense Team}
\date{\today}
\maketitle

\newpage

\article{Name.}\label{art:NAME}

The name of this organization shall be The Stevens Institute of Technology Cyber
Defense Team, herein referred to as \textit{The Stevens Cyber Defense Team} or
\textit{SCDT}, established under the Student Government Association at the
Stevens Institute of Technology.

\article{Purpose.}\label{art:GOALS}

The purpose this team shall be to:

\begin{enumerate}
\item Facilitate the growth of Stevens students in the field of computer
  security by working to give them opportunities to compete in security-focused
  competitions.
\item Bring knowledge and awareness of the greater cybersecurity community
  to Stevens.
\item Work to help maximize the ability of Stevens students to succeed in
  competitive environments in an engaging and productive manner.
\end{enumerate}

\article{Membership.}\label{art:MEMBERSHIP}

\section{General Membership.}\label{sec:GENERAL-MEMBERSHIP}

Membership in SCDT shall be open to all undergraduate students at The Stevens
Institute of Technology. Membership shall also be open to any graduate student
who previously participated in club events while taking an Undergraduate degree
at The Stevens Institute of Technology.

\section{Voting Membership.}\label{sec:VOTING-MEMBERSHIP}
% Since most competitions are online, and it's 2018, it seems silly to have X
% number of meetings be the deciding factor. On the other hand, that's what
% really shows dedication to the club. I decided to compromise. - DM
% EDIT: There's worry about quorum and people gaming the system so we're going
% back to being boring for now.

% Any member who meets any of the following requirements shall be considered a
% voting member:

% \begin{enumerate}
% \item The member has placed 1st, 2nd, or 3rd in a cybersecurity-focused
%   competition which the Stevens Cyber Defense Team has formally participated
%   in, or has been a part of a team which placed 1st, 2nd or, 3rd in a
%   cybersecurity-focused competition of the same nature. Participation and
%   placement must have occured within the past year.
% \item The member has attended 60\% or more of the total number of events,
%   general body meetings, or practices, starting from the beginning of the
%   semester to the time of voting.
% \item The member has previously held the position of President or Vice
%   President and is enrolled in an undergraduate or graduate course at Stevens.
% \end{enumerate}

Any Member who attends 60\% or more of the total number of events, general body
meetings, or practices, starting from the beginning of the semester, is eligible
to vote.

\article{Executive Board.}\label{art:EXECUTIVE-BOARD}

\section{Officers.}\label{art:OFFICERS}

% It's 2018, are conference calls official yet? - DM
The Executive Board shall consist of certain elected officers listed below and
will administer the affairs and programs of the team. The Executive Board will
consist of the President, Vice President, Secretary and Treasurer. The Executive
Board shall hold meetings once every month or when called by the President. The
Executive Board as a whole shall appoint one Committee on Student Interests
Representative(s). Elections shall occur yearly as specified by the Student
Government Association’s Unified Elections process, and as necessary to fill
vacancies.

\section{Duties of Officers.}\label{sec:DUTIES}

\begin{itemize}
\item President:
  \begin{enumerate}
  \item Preside over all meetings and events of SCDT.
  \item Be the official representative of SCDT in all student,
    faculty, and administrative matters. 
  \item Call and sanction regular or special meetings of the team and
    E-board.
  \item Form committees and appoint their respective chairs. 
  \item Submit a complete transition report of the position’s duties
    and accomplishments upon the completion of the term to the incoming
    Executive Board.
  \item Approve the formal entrance, registration, or involvement of
    SCDT with regards to cybersecurity competitions.
  \item Be the primary point of contact for hosts of other
    competitions and events.
  \end{enumerate}
  
\item Vice-President:
  \begin{enumerate}
  \item Assume all responsibilities of the President, in the absence
    thereof.
  \item Submit a complete transition report of position’s duties and
    accomplishments upon the completion of the term to the incoming
    Executive Board.
  \item Oversee and manage any code or document repositories
    maintained by SCDT.
  \item Perform all duties assigned by the President.
  \item Manage the inventory of the organization and coordinating
    on-campus storage of club materials and assets with the SGA.
  \item Submit a complete transition report of position’s duties and
    accomplishments upon the completion of the term to the incoming
    Executive Board.
  \end{enumerate}

\item Treasurer:
  \begin{enumerate}
  \item Maintain the records of all financial matters of the
    organization.
  \item Prepare a budget to submit to the President when requested.
  \item Submit a complete transition report of position’s duties and
    accomplishments upon the completion of the term to the incoming
    Executive Board.
  \item Perform all duties assigned by the President.
  \end{enumerate}

\item Secretary:
  \begin{enumerate}
  \item Perform the correspondence of SCDT.
  \item Manage the SCDT Slack (\url{https://ducks-ccdc.slack.com}) and
    the team mailing list.
  \item Record, store and distribute the minutes of all meetings and
    business discussed at events.
  \item Provide updated information for use in organizational
    activities and responsibilities as defined in the bylaws.
  \item Generate an agenda for all meetings.
  \item Submit a complete transition report of position’s duties and
    accomplishments upon the completion of the term to the incoming
    Executive Board.
  \item Keep track of progress made during competitions, including
    scores, points, and awards given, and participants, teams, or
    subteams involved.
  \item Perform all duties assigned by the President.
  \end{enumerate}
\end{itemize}

\section{Minor Board Officers.}\label{sec:MINOR-OFFICERS}

The Minor Board shall consist of certain elected officers listed below and
will assist the President in completing core team functions. The Minor Board
shall consist of the Red Coordinator and the Blue Coordinator. The Minor
Board is required be present at all meetings of the Executive Board or when
called by the President; if there is no need for the involvement of the Minor
Board at a specific function this requirement can be relaxed at the discretion
of the President.

\section{Duties of Minor Officers.}\label{sec:MINOR-DUTIES}

\begin{itemize}
\item Red Coordinator:
  \begin{enumerate}
  \item Discover new and exciting Capture the Flag or other offensive
    competitions for SCDT members to participate in, and propose
    entrance into these competitions to the Executive Board.
  \item Assist the President and Vice President in finding interested
    members to form teams in such competitions.
  \item Maintain and regularly check the team account on CTFTime
    (\url{https://ctftime.org/team/30063}).
  \item Assist the Secretary in keeping track of progress made during
    CTF competitions, including scores, points, and awards given, and
    participants or subteams involved.
  \end{enumerate}

\item Blue Coordinator:
  \begin{enumerate}
  \item Discover new and exciting cybersecurity competitions for SCDT
    members to participate in with the goal of defending networks or IT
    resources, and propose entrance into these competitions to the
    Executive Board.
  \item Assist the President and Vice President in finding interested
    members to form teams in such competitions.
  \item Assist the Secretary in maintaining documentation, strategy
    guides, programs, or other resources for use in defensive
    competitions.
  \item Assist the Secretary in keeping track of progress made during
    defensive competitions, including scores, points, and awards given,
    and participants or subteams involved. 
  \end{enumerate}
\end{itemize}

\section{Requirements of Officers.}\label{sec:REQUIREMENTS-OF-OFFICERS}

% The restriction is to try and avoid a situation where the President, etc. has
% been around for too long and nobody else knows how to do his job. - DM
Only voting members may hold Officer positions. Each member may hold a maximum
of one Officer position per semester and a maximum of two Officer positions
total. Officers serve a one year term, or serve until their successor is
elected.

\section{Exceptions to Requirements of Officers.}\label{sec:REQUIREMENTS-OF-OFFICERS-EXCEPTIONS}

% Can't have our club die again... - DM
In the event that not all Officer positions are filled and no more eligible
voting members are willing or available to fill any vacancies, the previously
stated requirements will be relaxed and any Member of the club may run for an
Officer position.

\section{Election of Officers.}\label{sec:ELECTION-OF-OFFICERS}

All elections shall be governed by policies set forth in the organization’s
parliamentary authority and in conjunction with the Unified Elections Policy of
the Student Government Association. All Officers shall be elected by vote of
eligible voting members, where quorum is present. Each candidate must be
nominated and seconded by an eligible voting member (which could include him--
or herself.) A vote by secret ballot must be held for each Offer position up for
election. The candidate receiving a simple majority shall be declared winner. In
the event of a tie, non-tying candidates are eliminated and a vote is held again
between tying candidates, with candidates allowed another opportunity to give a
speech, having a maximum length of 1 minute. The chair of the meeting will not
vote except in cases of a tie.

\section{Resignation of Office.}\label{sec:RESIGNATION-OF-OFFICE}

Should a member of the Executive Board choose to resign from office, this
individual must submit a formal notice of resignation to the Executive Board.
This member is responsible for the duties of their position for up to two weeks
or until a suitable replacement is chosen.

\section{Removal of Office.}\label{sec:REMOVAL-OF-OFFICE}

Any Officer of the Executive Board, who does not attend two consecutive
Executive Board meetings without valid reason, or is failing to perform their
duties, is liable to be removed from the Executive Board. To implement this
individual's removal, the Executive Board has the discretion to impeach the
member in question pending a simple majority approval of the voting members. A
majority vote is required to effect the removal.

\article{Committee on Student Interests Representative.}\label{art:COMMITTEE-ON-STUDENT-INTERESTS-REPRESENTATIVE}

The Committee on Student Interests Representative (also known as the ``RSO
Representative'') is responsible for attending meetings of the sub-committee of
the Committee on Student Interests to which the organization belongs. This may
be a member of the Executive Board, a General Body Member, or other, dependent
on the requirement of the organization’s Subcommittee.

\article{Parliamentary Authority.}\label{art:PARLIAMENTARY-AUTHORITY}

The rules contained in the current edition of Robert's Rules of Order Newly
Revised shall govern the organization in all cases to which they are applicable
and in which they are not inconsistent with these bylaws and any special rules
of order the team may adopt.

\article{Meetings.}\label{art:MEETINGS}

\section{Quorum.}\label{sec:QUORUM}

A majority of voting members shall constitute quorum.

\section{Meeting Time.}\label{sec:MEETING-TIME}

Meetings shall occur at the call of the President, or as resolved by the other
members of the Executives or Minor boards with approval of the President.

\section{Bylaws.}\label{sec:BYLAWS}

The team can propose bylaws to the Consitution which become ratified with the
approval of the SGA. No bylaw shall supersede or be inconsistent with this
constitution or the policies set forth by the SGA.

\article{Amendments.}\label{art:AMENDMENTS}

Amendments to this Constitution shall require a two-thirds majority, with
previous notice, of voting members to pass. Amendments must subsequently be
approved by the SGA. 

\article{Adoption.}\label{art:ADOPTION}

This Constitution shall become effective upon: 

\begin{enumerate}
\item Approval by the SCDT General Body.
\item Approval by the Student Government Association (SGA). 
\end{enumerate}

\end{document}